Filling templates or forms is a frequent and important task in many real-life situations. Examples include shift reports in manufacturing, patient intake forms in healthcare, and administrative documentation across various industries. However, converting unstructured spoken language into structured templates remains challenging, particularly when dealing with ambiguous or noisy inputs. Available form filling solutions struggle with ambiguous or noisy inputs, lack adaptability, and provide limited transparency.
To address these limitations, the focus of this thesis is on developing a modular, multi-agent system for speech-driven template filling using large language models (LLMs). This thesis presents Invox, a system that decomposes the task into five subtasks—transcription interpretation, retrieval of closely related past templates, field mapping, value inference, and result verification—handled by specialized LLM agents.
This thesis: (i) reviews existing solutions for automated form filling and identifies their key limitations; (ii) builds on existing techniques from LLM applications to create novel multi-agent approaches, implementing and comparing four architectural strategies: Single-LLM Full Input, Single-LLM One Field, Multi-LLM Full Input, and Multi-LLM One Field; (iii) evaluates these approaches using the MUC-4 dataset from literature, focusing on accuracy, consistency, latency, cost-efficiency, and modularity; and (iv) derives concrete instructions for the implementation of template filling applications, which will be of increasing importance as voice-driven interfaces become more prevalent.
The Invox system integrates Whisper for transcription and LLMs including GPT-4 and Gemini for template filling. Evaluation results reveal distinct trade-offs among the architectural strategies across accuracy, consistency, latency, cost-efficiency, and modularity, offering practical guidance for selecting appropriate approaches based on application requirements.

\textbf{Keywords: Large Language Models (LLMs), Multi-Agent Systems, Template Filling, Retrieval-Augmented Generation (RAG), Information Extraction, Prompt Engineering, Natural Language Understanding, Speech-to-Text Processing}