I would like to express my deepest gratitude to all those who supported and guided me throughout the development of this Master's thesis.

First and foremost, I am sincerely thankful to my internal supervising tutor, Verena Traubinger, for her dedicated support, timely feedback, and constructive suggestions throughout the entire process. Her patience, encouragement, and willingness to engage in critical discussions greatly contributed to both the conceptual and practical aspects of my work.

I would also like to extend my heartfelt appreciation to my external supervising tutor, Dr. Christoph Carl Kling, for his expert guidance and valuable insights. His technical knowledge and practical experience provided a crucial perspective that helped refine and strengthen the foundation of this thesis. His continuous motivation and thoughtful remarks challenged me to think critically and aim for a high-quality outcome.

Furthermore, I would like to thank the faculty members and academic staff of the program for creating an intellectually stimulating environment that inspired me to pursue research in this domain.

Special thanks also go to my friends and colleagues for their encouragement, helpful discussions, and emotional support during challenging times. I am especially grateful to my family for their unwavering belief in me, their unconditional support, and their motivation throughout my academic journey.

This thesis would not have been possible without the contributions and support of all these individuals. To each of them, I extend my sincere thanks.
